---
header-includes:
  \usepackage{fancyhdr}
   \pagestyle{fancy}
   \setlength{\headheight}{13.59999pt}
   \addtolength{\topmargin}{-1.59999pt}
   \fancyhf{}
   \fancypagestyle{plain}{\pagestyle{fancy}}
   \fancyhead[RO]{`r params$exam_number`}
   \fancyhead[L]{\emph{rexer}}
   \chead{\emph{rexer} package example - \emph{University of Granada}}
geometry: "left=2cm,right=2cm,top=3cm,bottom=2cm"
output:
  pdf_document:
    extra_dependencies: ["float"]
fontsize: 11pt
params:
  exam_number: 1
  exam_number_str: "01"
  examined: "01"
  exercises: ""
  all_exercises: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
```

```{r echo=F, results='asis'}
cat("<style>.figcaption{text-align:center;}</style>")
```


*Date*:_______ *Last name, first name*:_____________________________________


Example of an exam template to be used with the `rexer` package. In this section we can provide indications about the development of the exam.

If defined, the variable `params$examined` will contain the student's name. If not defined, it will contain the number of the generated exam instance (it will match the file name). This is its current value: `r params$examined`

This template presents the exercises one by one. The package only includes the statement of each exercise in the `params$exercises` vector variable. To present them, we have to loop through it or include them one by one to adapt their presentation, possibly including more indications.

Number of exercises: `r length(params$exercises)`

---

```{r, echo=FALSE, results='asis'}
for (i in seq_along(params$exercises)) {
  q <- paste0('**1.** ', params$exercises[i])
  cat(q)
}
```
